Multi-Agent Pathfinding with Matching using Increasing Cost Tree Search

### 2021-06-22 docs/paper.tex
Processed Jaap's feedback, added experimental data for simple pruning variant

	\title{Multi-Agent Pathfinding with Matching using Increasing Cost Tree Search}
	\author{
		Thom van der Woude$^1$\and
		Jesse Mulderij$^1$\and
		Mathijs de Weerdt$^1$\\
	}
	\date{%
		$^1$TU Delft\\
		t.b.vanderwoude@student.tudelft.nl\\\{j.mulderij, m.m.deweerdt\}@tudelft.nl\\[2ex]
		\today
	}

@@

	The experiments reported in \cite{ma2016} indicate that this method scales very well as the number of agents and the sizes of teams increase; however, because only 10\% of tiles is blocked in some of the grid maps they use and despite the fact that CBM performance on Kiva\cite{wurman2007} instances is also discussed, it remains to be seen how CBM performs in scenarios with more obstacles and more maze-like scenarios as included in the Moving AI benchmarks \cite{sturtevant2012} for MAPF.
	Nonetheless, the successful application of CBS to solving TAPF begs the question: \textit{can MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} or M* \cite{wagner2011} serve as the basis for a MAPFM algorithm?}

	\begin{wrapfigure}[19]{R}{.25\textwidth}
		\begin{minipage}{\linewidth}
			\centering\captionsetup[subfigure]{justification=centering}
			\includegraphics[width=\linewidth]{img/vertex-conflict}
			\subcaption{Vertex conflict}
			\label{fig:conflictsa}\par\vfill
			\includegraphics[width=0.75\linewidth]{img/edge-conflict}
			\subcaption{Edge conflict}
			\label{fig:conflictsb}
		\end{minipage}
		\vspace{-10pt}
		\caption{The two types of conflict (from Fig. 1 in \cite{stern2019})}\label{fig:conflicts}
	\end{wrapfigure}
	This work is the outcome of a search for algorithms which optimally solve MAPFM based on ICTS \footnote{To the knowledge of the author, to date, no such algorithm is described in the literature}, which is part of a study in which other algorithms addition to ICTS were taken as starting points for MAPFM algorithms. Two classes of ICTS-based algorithms were found: one based on exhaustive enumeration of matchings using a variant of ICTS as a subroutine, the other based on modifications to the ICT structure and its search. One exhaustive ICTS algorithm is compared to algorithms based on CBM \cite{ma2016}, M*\cite{wagner2011}, A*+OD+ID\cite{standley2010} and EPEA*\cite{goldenberg2014} respectively to put ICTS methods for MAPFM into a broader context.

	\section{Multi-agent pathfinding with matching} % Problem description
	\label{mapfm}
	The MAPFM problem is an extension of MAPF, a well-studied problem. Formally, a MAPF instance can be described as follows. Let $G = (V,E)$ be an undirected connected graph, with each $v\in V$ representing an obstacle-free tile on a 4-connected grid and each $e = (u,v)\in E$ representing a legal uniform-cost move between two such tiles. Let there be $k$ agents $a_1,\ldots,a_k$ with starting locations $s_1,\ldots,s_k$ and goals $g_1,\ldots,g_k$. For each agent $a_i$, a path $\pi_i$ from $s_i$ to $g_i$ is to be found such that all agents paths $\pi_i$ taken together are non-conflicting and therefore are a solution. In this work, non-conflicting means, in the conflict-terminology of \cite{stern2019}, that there are no vertex conflicts (and thus no edge conflicts) and no edge conflicts, as shown in Figure \ref{fig:conflicts}. Letting $\pi_i^t$ denote the $t$'th node of path $\pi_i$, this means that for $i\neq j$, for all $t$, $\pi_i^t\neq \pi_j^t$ and $(\pi_i^t \neq \pi_j^{t + 1})\lor(\pi_i^{t+1} \neq \pi_j^t)$. Given a solution $(\pi_1,\ldots,\pi_k)$, a vector of per-agent costs $(c_1,\ldots,c_k)$ can be found. For $\pi_i$, $c_i$ is defined as the time at which $a_i$ reaches $g_i$ for the last time and remains there, meaning that for $t \geq c_i$, $\pi_i^{t} = g_i$. One property of $c_i$ is that $c_i \geq c^*_i$ where $c^*_i$ is defined as the cost of $\pi^*_i$, the shortest path from $s_i$ to $g_i$ that can be computed using any optimal pathfinding algorithm. There are two common objectives in MAPF:
	\begin{itemize}
		\item The makespan: $\max_{i} c_i$
		\item The sum of individual costs (SIC): $\sum_i c_i$
	\end{itemize}
	In this work, following the definition of the TUSS relaxation in \cite{mulderij2020}, an optimal solution is defined as having minimal SIC. Note that $\sum_i c_i \geq \sum_i c^*_i$.
	\begin{wrapfigure}[10]{R}{.35\textwidth}
		\vspace{-10pt}
		\centering
		\includegraphics[width=\linewidth]{img/symmetries}
		\caption{Symmetric paths on a 4-connected grid\cite{harabor2010}}
		\label{fig:symmetries}
	\end{wrapfigure}
	The mapping from $(\pi_1,\ldots,\pi_k)$ to a SIC is surjective: many cost vectors $(c'_1,\ldots,c'_k)$ might add up to the same SIC as $(c_1,\ldots,c_k)$ and for a given agent $a_i$, there might be many equivalent paths $\pi'_i$ to the goal with cost $c_i$. On uniform-cost 4-grids in particular, there are often many equivalent and symmetrical paths\cite{harabor2010} (see Figure \ref{fig:symmetries}), which is why in single-agent pathfinding, symmetry-breaking methods such as Jump Point Search\cite{harabor2011} are used to speed up the search. In multi-agent pathfinding, having multiple paths per agent of the same cost can, in contrast, be a boon: it means that there are potentially more non-conflicting ways to combine paths of different agents.

	\subsection{Extending MAPF with matching}
	With the multi-agent pathfinding problem defined, the matching extension of MAPF (MAPFM) that is the subject of this paper can be described. The ICTS algorithm for MAPF and possible matching extensions of ICTS will be discussed in Section \ref{section:icts-matching}.

	Let there be $K$ teams $t_1,\ldots, t_K$, where $t_i$ consists of $k_i$ agents with start positions $s_1^i,\ldots,s_{k_i}^i$ together with an equal number of team goals $g_1^i,\ldots,g_{k_i}^i$. Within each team $t_i$, agents $a_j^i$ are to be \textit{matched} to a unique goal $g_k^i$, so that exactly one agent is assigned to each goal within team $i$; once all agents are matched to goals, for each agent $a_j^i$ matched to $g_k^i$, a path from $s_j^i$ to $g_k^i$ is to be found such that all agents paths taken together are non-conflicting and therefore make up a solution, similarly defined as for MAPF.

	As discussed in \cite{ma2016}, MAPFM generalizes both MAPF and anonymous MAPF, which is MAPF allowing an agent to move to any goal, a problem that can be solved in polynomial time.
	\section{Solving MAPF with Matching using ICTS} % Your contribution
	\label{section:icts-matching}
	Taking ICTS for MAPF as starting point, two methods to use ICTS for MAPFM were identified. The first method relies on a reduction from MAPFM to repeated MAPF: an optimal solution to MAPFM corresponds to a matching of agents to goals, so by exhaustively enumerating all matchings and solving these as MAPF instances, an optimal solution to the MAPFM instance can be found. In the second method, the increasing cost trees search itself is modified to allow an agent $a_j^i$ to be matched to any $g_k^i$. First, ICTS for MAPF and some common variants will be described. Next, derived MAPFM algorithms are introduced and properties of these algorithms and some variants are discussed. In Section \ref{experiments}, these will be compared experimentally.
	\subsection{Increasing Cost Tree Search}
	\label{icts}
	In Increasing Cost Tree Search\cite{sharon2011}, the two-step mapping from path combination to SIC described in Section \ref{mapfm} is reversed to search for a solution with minimal SIC. This is done by searching for cost vectors corresponding to increasing SIC on the top level and searching for non-conflicting path combinations (solutions) for each cost vector on the bottom level.

	\subsubsection{Top-level search}
	In the top-level search, all possible cost vectors for a given SIC are evaluated by searching an Increasing Cost Tree as depicted in \ref{fig:ict}, starting from $C^* = \sum_i c^*_i$ corresponding to a single root cost vector $(c^*_1,c^*_2,\ldots,c^*_k)$. This root has $k$ children $(c^*_1 + 1,c^*_2,\ldots,c^*_k),(c^*_1,c^*_2 + 1,\ldots,c^*_k),\ldots,(c^*_1,c^*_2,\ldots,c^*_k + 1)$ all of cost $C = C^* + 1$. Searching this ICT breadth-first corresponds to evaluating all possible cost vectors corresponding to increasing cost $C$ starting with $C^*$, guaranteeing optimality of a found solution. The number of cost vectors evaluated when searching up to nodes of cost $C^* + \Delta$ is $\mathcal{O}(k^\Delta)$. Node evaluation is done by a low-level search that searches for a solution $(\pi_1,\ldots,\pi_k)$ corresponding to the node costs $(c_1,\ldots,c_k)$.

@@

		\caption{Example of using ICTS to solve MAPF from \cite{sharon2011}}
		\label{fig:bottom}
	\end{figure}
	\subsubsection{Bottom-level search}
	Explicitly generating all paths to the goal for agent $a_i$ of cost $c_i$ is expensive: the number of paths is exponential in $c_i$. This is why in the low-level search of ICTS, multi-valued decision diagrams (MDDs) are used to compactly represent all paths per agent. For $a_i$ with a target cost $c_i$ (from the cost vector), $MDD_i^{c_i}$ can be generated by a breadth-first search on the $c_i$-steps time-expanded graph starting at $s_i$, followed by a process similar to the standard path reconstruction method used in A* but allowing multiple node parents. Storing the resulting paths in an MDD, which has at most $|V|$ nodes at each timestep or depth, avoids the cost of storing all paths explicitly and facilitates the efficient search of the $k$-agent space of path combinations \cite{sharon2011}.

	In Figure \ref{fig:bottom}, a problem with its corresponding ICT is shown, as well as the low-level search of the (solution) node $(3,2)$ using MDDs. Note that the second agent staying at node D after completing the path is modelled in its MDD also to ensure that the place remains blocked.

	Subfigure \ref{fig:mdds} illustrates how two or more MDDs can be combined: first, the root nodes are joined; next, the product of the children of both roots is taken and checked for conflicts. In \ref{fig:mdds}, a vertex conflict occurs and therefore this joint child can be removed from the MDD. If a $(B,A)$ node would be generated by the same root, $(A,B)$, this would similarly be an edge conflict and hence $(B,A)$ would also be removed from the joint MDD $MDD_{1,2}^{c_1,c_2}$. In the next layer, the process repeats with multiple parent nodes.

	In practice, joint MDDs are not explicitly constructed but instead, a depth-first search is used to search joint MDDs. This has the benefit of finding a path to the bottom of the joint MDD fast if one exists, while not constructing more of the joint MDD (which can get rather large) than is necessary for finding a solution.
	\subsubsection{ICTS with Independence Detection}
	Like other MAPF algorithms, ICTS can be embedded in the Independence Detection (ID) framework introduced by Standley in \cite{standley2010}. ID starts by assuming each agent is a group that can be assigned an optimal path independent of other groups. If group paths do conflict, they become one group that is planned together using a MAPF algorithm, in this case, ICTS, until no conflicts between groups occur. The goal of ID is to minimize $k'$, the size of the largest group that has to be planned. Optionally, a conflict avoidance table (CAT) can be maintained for use during the planning of groups. This records the paths planned by other groups and can facilitate tie-breaking in search that minimizes the number of conflicts; the CAT is omitted from Algorithm \ref{id-algo} for brevity but was implemented and used in experiments.
	\begin{algorithm}
		\begin{algorithmic}[1]
			\State \text{Assign each agent to a singleton group}
			\State \text{plan a path for each group}
			\Repeat
			\State \text{simulate execution of all paths until a conflict occurs}
			\State \text{merge two conflicting groups into a single group}
			\State \text{cooperatively plan new group}
			\Until{\text{no conflicts occur}}
			\State $solution\gets\text{paths of all groups combined}$
			\State \textbf{return solution}
		\end{algorithmic}
		\caption{Simple Independence Detection \cite{standley2010}} 
		\label{id-algo}
	\end{algorithm}
	\subsubsection{Pruning in ICTS}
	\label{pruning}
	In \cite{sharon2011}, in addition to the basic two-level solver, three pruning methods to speed up search are discussed, two of which were used in this work. All work by taking $j < k$ and applying the described method to each possible combination of $j$ out of $k$ agents. If no solution exists for any such combination, the full $k$-agent low-level search is not triggered. The two basic pruning methods are as follows.
	\begin{enumerate}
		\item Simple pruning: the $j$-agent MDD is searched using DFS for a solution.
		\item Enhanced pruning: the $j$-agent MDD is searched using BFS and when children are generated, for each agent, all children that do not appear in any unified node are removed from the MDD. In \ref{fig:mdds}, the $C$ node of $MDD_1$ would be removed as it cannot be unified with any node of $MDD_2$ at that level. 
	\end{enumerate}
	In addition, repeated enhanced pairwise pruning is described in which the enhanced pruning procedure is repeated for all combinations until a fixpoint is reached, which is when no child node is removed from any of the agent MDDs in an iteration. This was not used in this work.

	The full ICT-search algorithm including a pruning step is described by Algorithm \ref{icts-algo}. It is reproduced from \cite{sharon2011} for completeness. As noted before, this procedure can be used for planning groups in Algorithm \ref{id-algo}. In this work, triple-pruning was used and enhanced triple-pruning was taken as a baseline, as the conclusion in \cite{sharon2011} is that this often outperforms other variants.
	\begin{algorithm}
		\begin{algorithmic}[1]
			\Procedure{ICT-search}{MAPF instance}
			\State \text{Construct ICT root}
			\ForAll{\text{ICT nodes }$(c_1,\ldots,c_k)$\text{ in breadth-first order }} 
			\ForAll{\text{agents} $a_i$} 
			\text{Construct} $MDD_i^{c_i}$
			\EndFor
			\ForAll{$j$-\text{agent combinations} $(i_1,\ldots,i_j)$} 
			\State \text{Run node-pruning procedure with MDDs }$MDD_{i_1}^{c_{i_1}},\ldots,MDD_{i_j}^{c_{i_j}}$
			\If{\text{no solution was found for a combination in pruning}}
			\State \textbf{Break}\text{ and continue with next ICT node}
			\EndIf
			\EndFor
			\State \text{Search }$k$\text{-agent MDD space}
			\If{\text{solution was found}}
			\State \textbf{return solution}
			\EndIf
			\EndFor

			\EndProcedure
		\end{algorithmic}
		\caption{Increasing Cost Tree Search}
		\label{icts-algo}
	\end{algorithm}
	\subsection{Exhaustive ICTS}
	\label{exhaustive}
	For $K$ teams $t_1,\ldots,t_K$ of size $k_i$, there are in total $M = \prod_{i} k_i!$ matchings from team agents to team goals. Let $C_1$ through $C_M$ denote the optimal SIC costs of each MAPF instance corresponding to the instance, with $C_m = \infty$ for infeasible $m$. In order to find the optimal solution, $m$ with lowest $C_m$ has to be found, which requires all $M$ to be solved or found to be unfeasible, meaning that $\mathcal{O}(M)$ MAPF instances have to be solved. 
	\subsubsection{Bounded search}
	Once the first solution is found with cost $C$, this can be used in the next search as an (exclusive) upper-bound $B$ for the SIC of nodes that have to be searched. Formally, let $B_0 = \infty$ represent the initial SIC bound of the ICT search. After solving each $m$ with solution cost $C_m$, let $B_{m+1} = \min(B_m,C_m)$. By successively updating this $B$ in this manner, as more matchings are solved, the effort needed to solve the remaining matchings can be expected to be reduced significantly. With $C_m$ denoting the optimal SIC for matching $m$, this effort can be expressed as	
	\[\Delta_{m,\text{bounded}} = \min(B_m,C_m) - C^*_m = B_{m+1} - C^*_m\]
	This is proportional to the effort due to the complexity of the ICTS search for matching $m$, $\mathcal{O}(k^{\Delta_{m,\text{bounded}}})$.
	If $B_m < C^*_m$, only the root node will be generated to determine this so $\Delta_{m,\text{bounded}} = 0$.
	Using this, the number of ICT nodes searched in total becomes $\mathcal{O}(\sum_m k^{\Delta_{m,\text{bounded}}})$.
	\subsubsection{Ordered enumeration}
	\label{ordered-enum}
	To reduce the total effort as much as possible, the matchings $m$ can be enumerated and solved in increasing order of $C^*_m$. In this case, the effort per matching is monotonically non-increasing by Property \ref{monotonicity}. This induces a case in which this enumeration minimizes the number of nodes searched in total (Property \ref{cond-monoton-optim}). However, cases in which $\Delta_m$ of the first $m$'s searched is much higher could also be constructed, in which case this approach might cause more nodes to be processed in total than alternative methods. Therefore, this ordered enumeration remains a heuristic improvement that works well in practice, as shown in Section \ref{experiments}.

@@

	All algorithms are implemented in Python 3.9 to avoid performance differences as often seen between interpreted versus compiled languages; however, CBM\cite{baauw2021} in experiment 2 does use an SSP solver implemented in C++ as a subroutine. Nonetheless, the comparison in this experiment is more coarse-grained as performance differences are sometimes subtle and could potentially be explained by slight implementation optimizations rather than algorithmic properties.

@@

	The benefit of using ID together with ordered enumeration is less clear. Ordered enumeration with ID performs much better in \ref{fig:i-75-3-p}, a setting with more obstacles and more teams, but ordered enumeration without ID on the other hand is superior in an open setting with a single team (\ref{fig:i-25-1-p}). The overhead associated with the various planning and merging steps (see Algorithm \ref{id-algo}) could be the cause the slowdown observed once $M$ grows large (\ref{fig:i-25-1-p},\ref{fig:i-75-1-p}); once the upper bound is tightened, ICTs only have to be searched shallowly so there is no point in going through the steps of ID. This explains why no speedup is seen, as ICTS-m between and ICTS-m+ID. Another factor is that if all agents belong to the same team, it is somewhat unlikely that there will a significant benefit to using ID, as agents from the same team planned independently often route to the same goal.

>>>>

	\title{Multi-Agent Pathfinding with Matching using Increasing Cost Tree Search}
	\author{
		Thom van der Woude$^1$\\[2ex]
		Supervisors: Jesse Mulderij$^1$ Mathijs de Weerdt$^1$
	}
	\date{%
		$^1$TU Delft\\
		t.b.vanderwoude@student.tudelft.nl\\\{j.mulderij, m.m.deweerdt\}@tudelft.nl\\[2ex]
		\today
	}

@@

	The experiments reported in \cite{ma2016} indicate that this method scales very well as the number of agents and the sizes of teams increase; however, because only 10\% of tiles is blocked in some of the grid maps they use and despite the fact that CBM performance on Kiva\cite{wurman2007} instances is also discussed, it remains to be seen how CBM performs in scenarios with more obstacles and more maze-like scenarios as included in the Moving AI benchmarks \cite{sturtevant2012} for MAPF.
	Nonetheless, the successful application of CBS to solving TAPF begs the question: \textit{can MAPF algorithms such as Increasing Cost Tree Search (ICTS) \cite{sharon2011} serve as the basis for a MAPFM algorithm?}

	\begin{wrapfigure}[19]{R}{.25\textwidth}
		\begin{minipage}{\linewidth}
			\centering\captionsetup[subfigure]{justification=centering}
			\includegraphics[width=\linewidth]{img/vertex-conflict}
			\subcaption{Vertex conflict}
			\label{fig:conflictsa}\par\vfill
			\includegraphics[width=0.75\linewidth]{img/edge-conflict}
			\subcaption{Edge conflict}
			\label{fig:conflictsb}
		\end{minipage}
		\vspace{-10pt}
		\caption{The two types of conflict (from Fig. 1 in \cite{stern2019})}\label{fig:conflicts}
	\end{wrapfigure}
	This work is the outcome of a search for algorithms which optimally solve MAPFM based on ICTS \footnote{To the knowledge of the author, to date, no such algorithm is described in the literature}, which is part of a study in which other algorithms addition to ICTS were taken as starting points for MAPFM algorithms. Two classes of ICTS-based algorithms were found: one based on exhaustive enumeration of matchings using a variant of ICTS as a subroutine, the other based on modifications to the Increasing Cost Tree (ICT) structure and its search. One exhaustive ICTS algorithm is compared to algorithms based on CBM \cite{ma2016}, M*\cite{wagner2011}, A*+OD+ID\cite{standley2010} and EPEA*\cite{goldenberg2014} to put ICTS methods for MAPFM into a broader context.

	\section{Multi-agent pathfinding with matching} % Problem description
	\label{mapfm}
	The MAPFM problem is an extension of MAPF, a well-studied problem. Formally, a MAPF instance can be described as follows. Let $G = (V,E)$ be an undirected graph, with each $v\in V$ representing an obstacle-free tile on a 4-connected grid and each $e = (u,v)\in E$ representing a legal uniform-cost move between two such tiles. Let there be $k$ agents $a_1,\ldots,a_k$ with starting locations $s_1,\ldots,s_k$ and goals $g_1,\ldots,g_k$. For each agent $a_i$, a path $\pi_i$ from $s_i$ to $g_i$ is to be found such that all agents' paths $\pi_i$ taken together are non-conflicting and therefore are a solution. In this work, non-conflicting means, in the conflict-terminology of \cite{stern2019}, that there are no vertex conflicts and no edge conflicts, as shown in Figure \ref{fig:conflicts}. Letting $\pi_i^t$ denote the $t$'th node of path $\pi_i$, this means that for $i\neq j$, for all $t$, $\pi_i^t\neq \pi_j^t$ and $(\pi_i^t \neq \pi_j^{t + 1})\lor(\pi_i^{t+1} \neq \pi_j^t)$. Given a solution $(\pi_1,\ldots,\pi_k)$, a vector of per-agent costs $(c_1,\ldots,c_k)$ can be found. For $\pi_i$, $c_i$ is defined as the time at which $a_i$ reaches $g_i$ for the last time and remains there, meaning that for $t \geq c_i$, $\pi_i^{t} = g_i$. One property of $c_i$ is that $c_i \geq c^*_i$ where $c^*_i$ is defined as the cost of $\pi^*_i$, the shortest path from $s_i$ to $g_i$ that can be computed using any optimal pathfinding algorithm. There are two common objectives in MAPF:
	\begin{itemize}
		\item The makespan: $\max_{i} c_i$
		\item The sum of individual costs (SIC): $\sum_i c_i$
	\end{itemize}
	In this work, following the definition of the TUSS relaxation in \cite{mulderij2020}, an optimal solution is defined as having minimal SIC. Note that $\sum_i c_i \geq \sum_i c^*_i$.
	\begin{wrapfigure}[10]{R}{.35\textwidth}
		\vspace{-10pt}
		\centering
		\includegraphics[width=\linewidth]{img/symmetries}
		\caption{Symmetric paths on a 4-connected grid\cite{harabor2010}}
		\label{fig:symmetries}
	\end{wrapfigure}
	The mapping from $(\pi_1,\ldots,\pi_k)$ to a SIC is surjective: many cost vectors $(c'_1,\ldots,c'_k)$ might add up to the same SIC as $(c_1,\ldots,c_k)$ and for a given agent $a_i$, there might be many equivalent paths $\pi'_i$ to the goal with cost $c_i$. On uniform-cost 4-grids in particular, there are often many equivalent and symmetrical paths\cite{harabor2010} (see Figure \ref{fig:symmetries}), which is why in single-agent pathfinding, symmetry-breaking methods such as Jump Point Search\cite{harabor2011} are used to speed up the search. In multi-agent pathfinding, having multiple paths per agent of the same cost can, in contrast, be a boon: it means that there are potentially more non-conflicting ways to combine paths of different agents.

	\subsection{Extending MAPF with matching}
	With the multi-agent pathfinding problem defined, the matching extension of MAPF (MAPFM) that is the subject of this paper can be described.

	Let there be $K$ teams $t_1,\ldots, t_K$, where $t_i$ consists of $k_i$ agents with start positions $s_1^i,\ldots,s_{k_i}^i$ together with an equal number of team goals $g_1^i,\ldots,g_{k_i}^i$. Within each team $t_i$, agents $a_j^i$ are to be \textit{matched} to a unique goal $g_k^i$, so that exactly one agent is assigned to each goal within team $i$; once all agents are matched with goals, for each agent $a_j^i$ matched with $g_k^i$, a path from $s_j^i$ to $g_k^i$ is to be found such that all agents' paths taken together are non-conflicting and therefore make up a solution, similarly defined as for MAPF.

	As discussed in \cite{ma2016}, MAPFM generalizes both MAPF and anonymous MAPF, which is MAPF allowing an agent to move to any goal, a problem that can be solved in polynomial time.
	\section{Solving MAPF with Matching using ICTS} % Your contribution
	\label{section:icts-matching}
	In this section, taking ICTS for MAPF as a starting point, two methods to use ICTS for MAPFM are described. The first method relies on a reduction from MAPFM to repeated MAPF: an optimal solution to MAPFM corresponds to a matching of agents to goals, so by exhaustively enumerating all matchings and solving these as MAPF instances, an optimal solution to the MAPFM instance can be found. In the second method, the ICT search itself is modified to allow an agent $a_j^i$ to be matched to any $g_k^i$.
	\subsection{Increasing Cost Tree Search}
	\label{icts}
	In Increasing Cost Tree Search\cite{sharon2011}, the two-step mapping from path combination to SIC described in Section \ref{mapfm} is reversed to search for a solution with minimal SIC. This is done by searching for cost vectors corresponding to increasing SIC on the top level and searching for non-conflicting path combinations (solutions) for each cost vector on the bottom level.

	\subsubsection{Top-level search}
	In the top-level search, all possible cost vectors for a given SIC are evaluated by searching an Increasing Cost Tree as depicted in Figure \ref{fig:ict}, starting from $C^* = \sum_i c^*_i$ corresponding to a single root cost vector $(c^*_1,c^*_2,\ldots,c^*_k)$. This root has $k$ children $(c^*_1 + 1,c^*_2,\ldots,c^*_k),(c^*_1,c^*_2 + 1,\ldots,c^*_k),\ldots,(c^*_1,c^*_2,\ldots,c^*_k + 1)$ all of cost $C = C^* + 1$. Searching this ICT breadth-first corresponds to evaluating all possible cost vectors corresponding to increasing cost $C$ starting with $C^*$, guaranteeing optimality of a found solution. The number of cost vectors evaluated when searching up to nodes of cost $C^* + \Delta$ is $\mathcal{O}(k^\Delta)$. Node evaluation is done by a low-level search that searches for a solution $(\pi_1,\ldots,\pi_k)$ corresponding to the node costs $(c_1,\ldots,c_k)$.

@@

		\caption{Example of using ICTS to solve MAPF from \cite{sharon2011}}
		\label{fig:bottom}
	\end{figure}
	\subsubsection{Bottom-level search}
	Explicitly generating all paths to the goal for agent $a_i$ of cost $c_i$ is expensive: the number of paths is exponential in $c_i$. This is why in the low-level search of ICTS, multi-valued decision diagrams (MDDs) are used to compactly represent all paths per agent. For agent $a_i$ with a target cost $c_i$ (from the cost vector), $MDD_i^{c_i}$ can be generated by a breadth-first search on the $c_i$-steps time-expanded graph starting at $s_i$, followed by a process similar to the standard path reconstruction method used in A* but allowing multiple node parents. Storing the resulting paths in an MDD, which has at most $|V|$ nodes at each timestep or depth, avoids the cost of storing all paths explicitly and facilitates the efficient search of the $k$-agent space of path combinations \cite{sharon2011}.

	In Figure \ref{fig:bottom}, a problem with its corresponding ICT is shown, as well as the low-level search of the (solution) node $(3,2)$ using MDDs. Note that the second agent staying at node D after completing the path is also modelled in its MDD to ensure that the place remains blocked.

	Subfigure \ref{fig:mdds} illustrates how two or more MDDs can be combined: first, the root nodes are joined; next, the product of the children of both roots is taken and checked for conflicts. In \ref{fig:mdds}, a vertex conflict occurs and therefore this joint child can be removed from the MDD. If a $(B,A)$ node would be generated by the same root, $(A,B)$, this would be an edge conflict and hence $(B,A)$ would also be removed from the joint MDD $MDD_{1,2}^{c_1,c_2}$. In the next layer, the process repeats with multiple parent nodes.

	In practice, joint MDDs are not explicitly constructed but instead, a depth-first search is used to search joint MDDs. This has the benefit of finding a path to the bottom of the joint MDD fast if one exists, while not constructing more of the joint MDD than is necessary for finding a solution, which can get rather large.
	\subsubsection{ICTS with Independence Detection}
	Like other MAPF algorithms, ICTS can be embedded in the Independence Detection (ID) framework introduced by Standley in \cite{standley2010}. ID starts by assuming each agent is a group that can be assigned an optimal path independent of other groups. If group paths do conflict, they become one group that is planned together using a MAPF algorithm, in this case, ICTS, until no conflicts between groups occur. The goal of ID is to minimize $k'$, the size of the largest group that has to be planned. Optionally, a conflict avoidance table (CAT) can be maintained for use during the planning of groups. This records the paths planned by other groups and can facilitate tie-breaking in search that minimizes the number of conflicts; the CAT is omitted from Algorithm \ref{id-algo} for brevity but was implemented and used in experiments.
	\begin{algorithm}
		\begin{algorithmic}[1]
			\State \text{Assign each agent to a singleton group}
			\State \text{plan a path for each group}
			\Repeat
			\State \text{simulate execution of all paths until a conflict occurs}
			\State \text{merge two conflicting groups into a single group}
			\State \text{cooperatively plan new group}
			\Until{\text{no conflicts occur}}
			\State $solution\gets\text{paths of all groups combined}$
			\State \textbf{return solution}
		\end{algorithmic}
		\caption{Simple Independence Detection \cite{standley2010}} 
		\label{id-algo}
	\end{algorithm}
	\subsubsection{Pruning in ICTS}
	\label{pruning}
	In \cite{sharon2011}, in addition to the basic two-level solver, three pruning methods to speed up search are discussed, two of which were used in this work. These methods rely on the fact that if no solution exists for any combination of $j$ out of $k$ agents with $j < k$, no solution exists for all $k$ agents. If any such combination is found for a node, there is no need to search the $k$-agent MDD so the next ICT node can be considered. The three pruning methods are as follows.
	\begin{enumerate}
		\item Simple pruning: for all combinations of $j$ out of $k$ agents, the $j$-agent MDD is searched using DFS for a solution.
		\item Enhanced pruning: for all combinations of $j$ out of $k$ agents, the $j$-agent MDD is searched using BFS and when children are generated, for each agent, all children that do not appear in any unified node are removed from the MDD. In \ref{fig:mdds}, the $C$ node of $MDD_1$ would be removed as it cannot be unified with any node of $MDD_2$ at that level.
		\item Repeated enhanced pruning: the enhanced pruning procedure is repeated until a fixpoint is reached, which is when no child node is removed from any of the agent MDDs in an iteration. This was not used in this work. 
	\end{enumerate}
	The full ICTS algorithm including a pruning step is described by Algorithm \ref{icts-algo}. It is reproduced from \cite{sharon2011} for completeness. As noted before, this procedure can be used for planning groups in Algorithm \ref{id-algo}. In this work, triple-pruning ($j=3$) was used and enhanced triple-pruning was taken as a baseline, as the conclusion in \cite{sharon2011} is that this often outperforms other variants.
	\begin{algorithm}
		\begin{algorithmic}[1]
			\Procedure{ICT-search}{MAPF instance}
			\State \text{Construct ICT root}
			\ForAll{\text{ICT nodes }$(c_1,\ldots,c_k)$\text{ in breadth-first order }} 
			\ForAll{\text{agents} $a_i$} 
			\text{Construct} $MDD_i^{c_i}$
			\EndFor
			\ForAll{$j$-\text{agent combinations} $(i_1,\ldots,i_j)$} 
			\State \text{Run node-pruning procedure with MDDs }$MDD_{i_1}^{c_{i_1}},\ldots,MDD_{i_j}^{c_{i_j}}$
			\If{\text{no solution was found for a combination in pruning}}
			\State \textbf{Break}\text{ and continue with next ICT node}
			\EndIf
			\EndFor
			\State \text{Search }$k$\text{-agent MDD space}
			\If{\text{solution was found}}
			\State \textbf{return solution}
			\EndIf
			\EndFor

			\EndProcedure
		\end{algorithmic}
		\caption{Increasing Cost Tree Search}
		\label{icts-algo}
	\end{algorithm}
	\subsection{Exhaustive ICTS}
	\label{exhaustive}
	For $K$ teams $t_1,\ldots,t_K$ of size $k_i$, there are in total $M = \prod_{i} k_i!$ matchings from team agents to team goals. Let $C_1$ through $C_M$ denote the optimal SIC costs of each MAPF instance corresponding to the MAPFM instance, with $C_m = \infty$ for infeasible $m$. In order to find the optimal solution, $m$ with lowest $C_m$ has to be found, which requires all $M$ to be solved or found to be unfeasible, meaning that $\mathcal{O}(M)$ MAPF instances have to be solved. 
	\subsubsection{Bounded search}
	Once a solution is found for matching $m$ with cost $C_m$, this can be used in the next search as an (exclusive) upper-bound $B$ for the SIC of nodes that have to be searched. Formally, let $B_0 = \infty$ represent the initial SIC bound of the ICT search. After solving each $m$ with solution cost $C_m$, let $B_{m+1} = \min(B_m,C_m)$. By successively updating this $B$ in this manner, as more matchings are solved, the effort needed to solve the remaining matchings can be expected to be reduced significantly. With $C_m$ denoting the optimal SIC for matching $m$, this effort can be expressed as	
	\[\Delta_{m,\text{bounded}} = \min(B_m,C_m) - C^*_m = B_{m+1} - C^*_m\]
	This is proportional to the effort due to the complexity of the ICTS search for matching $m$, $\mathcal{O}(k^{\Delta_{m,\text{bounded}}})$.
	If $B_m < C^*_m$, only the root node will be generated to determine this so $\Delta_{m,\text{bounded}} = 0$.
	Using this, the number of ICT nodes searched in total becomes $\mathcal{O}(\sum_m k^{\Delta_{m,\text{bounded}}})$.
	\subsubsection{Ordered enumeration}
	\label{ordered-enum}
	To reduce the total effort, the matchings $m$ can be enumerated and solved in increasing order of $C^*_m$. In this case, the effort per matching is monotonically non-increasing by Property \ref{monotonicity}. This induces a case in which this enumeration minimizes the number of nodes searched in total (Property \ref{cond-monoton-optim}). However, cases in which $\Delta_m$ of the first $m$'s searched is much higher could also be constructed, in which case this approach might cause more nodes to be processed in total than alternative methods. Therefore, this ordered enumeration remains a heuristic improvement that works well in practice, as shown in Section \ref{experiments}.

@@

	All algorithms are implemented in Python 3.9 to avoid performance differences as often seen between interpreted versus compiled languages; however, CBM\cite{baauw2021} in experiment 2 does use an SSP solver implemented in C++ as a subroutine. The comparison in this experiment is more coarse-grained as performance differences are sometimes subtle and could potentially be explained by slight implementation optimizations rather than algorithmic properties.

@@

	The benefit of using ID together with ordered enumeration is less clear. Ordered enumeration with ID performs much better in \ref{fig:i-75-3-p}, a setting with more obstacles and more teams, but ordered enumeration without ID on the other hand is superior in an open setting with a single team (\ref{fig:i-25-1-p}). The overhead associated with the various planning and merging steps (see Algorithm \ref{id-algo}) could be the cause the slowdown observed once $M$ grows large (\ref{fig:i-25-1-p},\ref{fig:i-75-1-p}); once the upper bound is tightened, ICTs only have to be searched shallowly so there is no point in going through the steps of ID. This explains why no speedup is seen, as  between ICTS-m and ICTS-m+ID. Another factor is that if all agents belong to the same team, it is somewhat unlikely that there will a significant benefit to using ID, as agents from the same team planned independently often route to the same goal.
